%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ============================================================================== %
% ============================================================================== %
%            STOP HERE - DO NOT EDIT ANYTHING ABOVE THIS LINE                    %
% ============================================================================== %
% ============================================================================== %

\begin{document}

%-----------HEADER-----------
\begin{center}
    \textbf{\Huge \scshape Pang Yi Hahn} \\ \vspace{1pt}
    \small +65 8835 7353 $|$ \href{mailto:yihahn.pang@gmail.com}{\underline{yihahn.pang@gmail.com}} $|$ 
    \href{https://linkedin.com/in/pangyihahn}{\underline{linkedin.com/in/pangyihahn}} $|$
    \href{https://github.com/pangyihahn}{\underline{github.com/pangyihahn}} $|$
    \href{https://pangyihahn.com}{\underline{pangyihahn.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science (OMSCS)}{Expected Aug. 2026 -- Present}

    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Bachelor of Engineering (Hons), Environmental Engineering \& Data Analytics}{Aug. 2022 -- June 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Academics:} Cumulative GPA: 4.46/5.0 (Distinction) $|$ ASEAN Scholarship Recipient}
        \resumeItem{\textbf{Leadership \& Athletics:} Won 7 athletic medals representing NUS College; Co-organized a 2-week symposium hosting 150 students from 10 ASEAN countries; Launched campus-wide BYOC waste-reduction campaign.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Engineer Intern}{Jan. 2026 -- May 2026}
      {Climate Impact X (CIX)}{Singapore}
      \resumeItemListStart
        \resumeItem{\textbf{Invited to return for a second term} based on technical ownership and effective communication.}
        \resumeItem{Architected the migration of legacy SQL pipelines to dbt, establishing a materialization strategy that reduced Snowflake compute time by 86\% (from 66 to 9 mins).}
        \resumeItem{Enhanced pipeline reliability by developing comprehensive dbt tests, integrating custom Microsoft Teams alerts to surface business logic warnings without disrupting Airflow runs.}
        \resumeItem{Spearheaded AI integration by deploying a Microsoft Fabric Data Agent (FDA) within M365, utilizing Snowflake change tracking for automated data refreshes and natural language querying.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineer Intern}{Jan. 2025 -- June 2025}
      {Climate Impact X (CIX)}{Singapore}
      \resumeItemListStart
        \resumeItem{Built 18 automated ETL pipelines (Airflow, PySpark, Azure) to ingest data from multiple sources into Snowflake and MongoDB, saving 10+ manual hours weekly.}
        \resumeItem{Refactored Snowflake schema by consolidating 40+ views into a Medallion Architecture, significantly improving data lineage and eliminating schema redundancies.}
        \resumeItem{Engineered 2 CI/CD pipelines (Bash, Azure DevOps) to automate Azure deployments and ensure strict environment parity.}
      \resumeItemListEnd

    \resumeSubheading
      {Environmental Engineer Intern}{May 2024 -- Aug. 2024}
      {Carbon GPT}{Singapore}
      \resumeItemListStart
        \resumeItem{Developed 4 LLM prototypes (Streamlit, Groq API) to automate manual processes; prototypes were subsequently utilized in successful sales pitches to UOB, CIMB, and Bursa.}
        \resumeItem{Engineered an ETL pipeline (Python, PostgreSQL) to process and optimize over 1.5M+ records, ensuring robust database scalability for downstream analysis.}
        \resumeItem{Led client engagements to gather technical requirements, ensuring product alignment with direct user feedback.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Local Snowflake SQL Transpiler} $|$ \emph{DuckDB, sqlglot, Python}}{}
          \resumeItemListStart
            \resumeItem{Developed a local Snowflake SQL execution environment allowing developers to conduct fast, cost-free query testing and ensuring cross-database compatibility.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Real-Time Stock Streaming Dashboard} $|$ \emph{Kafka, Streamlit}}{}
          \resumeItemListStart
            \resumeItem{Developed a real-time stock trading simulator utilizing event streaming to visualize high-frequency market data.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Weather Analytics ELT Pipeline} $|$ \emph{AWS Lambda, S3, Redshift}}{}
          \resumeItemListStart
            \resumeItem{Built a fully cloud-native ELT pipeline to extract, load, and analyze historical Singapore weather trends.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{SGX Derivatives Data Downloader CLI} $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Built a Python CLI tool to automate the retrieval of SGX derivatives data, complete with automated retry mechanisms, logging, and job scheduling support.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python (Pandas, NumPy, FastAPI), SQL, Java, R} \\
     \textbf{Data Stack}{: Apache Spark (PySpark), Apache Airflow, Kafka, dbt, Snowflake, Databricks, PostgreSQL, MongoDB} \\
     \textbf{Cloud, ML \& BI}{: AWS, Azure, Microsoft Fabric, Docker, Git, CI/CD, PyTorch, Scikit-learn, Power BI} \\
     \textbf{Certifications}{: AWS Certified Cloud Practitioner, Databricks Certified Data Engineer Associate}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
